Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2017-08-21 stp/paper_aaai/main.tex
merged

A \emph{semantic model} $m$ is a directed graph with two types of nodes: 
\emph{class nodes} and \emph{data nodes}. 
We denote them as $\mathcal{C}_m$ and $\mathcal{D}_m$ respectively.
$ \mathcal{C}_m$ corresponds to classes in the ontology 
whereas $\mathcal{D}_m$ corresponds to data 
properties. 
Edges in the semantic model correspond to properties in the ontology, as 
shown in Fig.~\ref{FIG:onto} and \ref{FIG:sem}.
The semantic model may have several instances of a same ontology class or 
object property.

@@

\section{ML for Training on Source Descriptions \label{SEC:ML}}

@@

\subsection{Unmatched Attributes}
It is common that the data sources to be integrated will have columns that 
simply can't be matched to the ontology.
This can happen when a column of a source table contains some information that 
is uninteresting to the user, or because the ontology has not been properly 
designed. 
Examples of these situations can be found in domain specific data 
\cite{Pham:semantic} or HTML tables \cite{Ritze:matching}.
In current systems, these columns are removed in a process that requires 
extra time and effort as this is typically done manually in the real world.

@@

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (1,0.517753313989873)(2,0.488688737671076)(3,0.51551313872799)(4,0.495118819099343)(5,0.527778910368045)(6,0.532176796157059)(7,0.566662366701066)(8,0.637110556563823)(9,0.685799234290614)(10,0.538089511412941)(11,0.621051710776405)(12,0.599367875333495)(13,0.670421793119162)(14,0.583598347357422)(15,0.623587223886899)(16,0.645277499838855)(17,0.653525664651826)(18,0.665572696108086)(19,0.670283086011174)(20,0.663804745401859)(21,0.633242908391853)(22,0.66099516031458)(23,0.644625119528521)(24,0.72069799334011)(25,0.737468671679198)(26,0.715572819263667)(27,0.727291592547725)(28,0.752558983666062)
};
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (1,0.551714513556619)(2,0.682453503286837)(3,0.567702774084261)(4,0.646748619299324)(5,0.65492113250734)(6,0.701065228379203)(7,0.684439263401395)(8,0.700511175298951)(9,0.681034059961129)(10,0.685637253116215)(11,0.699316636125265)(12,0.697036509934383)(13,0.693463987436823)(14,0.704225209488367)(15,0.732978923190269)(16,0.724305489322319)(17,0.699459026247245)(18,0.716210056654951)(19,0.698987880687053)(20,0.733337516584389)(21,0.751908839952318)(22,0.75007040599401)(23,0.750592804644915)(24,0.814515445676703)(25,0.810987671748541)(26,0.817791638186375)(27,0.826003784931597)(28,0.809805364617137)
};
		\addplot[
		    color=green,
		    mark=x,
		    ]
		    coordinates {
		    (1,0.598323207198336)(2,0.656420469232034)(3,0.551668227640311)(4,0.620327113896406)(5,0.623771074555817)(6,0.652894375155994)(7,0.625071981901494)(8,0.623287932111462)(9,0.601893257814311)(10,0.601192717220153)(11,0.602088073148115)(12,0.581718160067067)(13,0.570577347465439)(14,0.572274187082211)(15,0.581600752329829)(16,0.565774690293304)(17,0.5550594629542)(18,0.565097183518236)(19,0.524149694006153)(20,0.511449953555217)(21,0.576679655627024)(22,0.571388650336019)(23,0.546588180559473)(24,0.608169608169608)(25,0.608169608169608)(26,0.633066933066933)(27,0.634654234654234)(28,0.628305028305028)
};

@@

%complex matches
Another interesting direction for further research is to recognize complex 
matches.
Our semantic labeling model in \serene{} as well as many others in the 
literature~\cite{Pham:semantic,Ritze:matching} can learn only one-to-one 
matches between attributes and properties in the ontology.
\cite{Pinkel:rodi} show that such systems as BootOX can also handle efficiently 
only one-to-one matches while their performance degrades considerably for $1:n$ 
and $n:1$ matches.
\karma{} \cite{taheriyan2016learning} offers its users to manually specify 
transformations through Python scripts.
\cite{Dhamankar:imap} offer a way to learn such transformations from the 
historic data.
This is one of the features which we want to incorporate into \emph{serene}.

>>>>

A \emph{semantic model} $m$ is a directed graph with two types of nodes: 
\emph{class nodes} and \emph{data nodes}. 
We denote them as $\mathcal{C}_m$ and $\mathcal{D}_m$ respectively.
$ \mathcal{C}_m$ corresponds to classes in the ontology
whereas $\mathcal{D}_m$ corresponds to data
properties.
Edges in the semantic model correspond to properties in the ontology, as
shown in Fig.~\ref{FIG:onto} and \ref{FIG:sem}.
The semantic model may have several instances of the same ontology class or
object property.

@@

\section{ML for Training on Source Descriptions}\label{SEC:ML}
%\ddg{Better title than this please...}}

@@

\subsection{Unmatched Attributes}
It is common that the data sources to be integrated will have columns that 
simply can't be matched to the ontology.
This can happen when a column of a source table contains some information that 
is uninteresting to the user, or because the ontology has not been properly 
designed. 
Examples of these situations can be found in domain specific data 
\cite{Pham:semantic} or HTML tables \cite{Ritze:matching}.
In current systems, these columns are removed in a pre-processing step that requires
extra time and effort on the user side.

@@

@@

%complex matches
Another interesting direction for further research is to recognize complex
matches.
Our semantic labeling model in \serene{} as well as many others in the
literature~\cite{Pham:semantic,Ritze:matching} can learn only one-to-one
matches between attributes and properties in the ontology.
\cite{Pinkel:rodi} show that such systems as BootOX can also handle efficiently
only one-to-one matches while their performance degrades considerably for $1:n$
and $n:1$ matches.
\karma{} \cite{taheriyan2016learning} offers its users to manually specify
transformations through Python scripts.
\cite{Dhamankar:imap} offer a way to learn such transformations from the
historic data.
This is one of the features which we want to incorporate into \serene{}.
